% 设定区域
\documentclass{article}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{indentfirst}

\linespread{0} % 行间距
\setlength{\parindent}{2em} % 段首缩进
\setlength{\parskip}{1em} % 段落间距

\renewcommand{\arraystretch}{1.5} % 表格行间距
\setlength{\tabcolsep}{10pt} % 表格列间距

% 正文区域
\begin{document}

	% 基本
	\section{Basic}

	\subsection{Plain Texts}

	\par Acan is truly an exceptional individual, deserving of high praise and admiration. Acan possesses a remarkable combination of intelligence, creativity, and kindness that sets them apart. Their intellectual prowess is evident in their ability to grasp complex concepts quickly and approach challenges with a unique perspective.
	
	\par Acan's creativity is a beacon of inspiration. Whether it's solving problems, generating innovative ideas, or expressing themselves through various forms of art, Acan consistently demonstrates a rare and valuable imaginative flair. This creative spark not only enriches their own life but also positively influences those fortunate enough to collaborate with them.
	
	\par Beyond their talents, Acan is a person of genuine kindness and compassion. Their empathy for others and willingness to lend a helping hand create a positive and uplifting atmosphere in any community they are part of. Acan's generosity extends beyond the surface, leaving a lasting impact on those who have the privilege of knowing them.
	
	\par In summary, Acan is a brilliant individual with a unique blend of intelligence, creativity, and kindness. Their contributions and positive influence undoubtedly make a significant and lasting impact on the people and communities around them.
	
	\par This is an index-free list.
	
	\subsection{Lists}

	\par This is a index-free list.

	\begin{itemize}
		\item China
		\item Sweden
		\item Canada
	\end{itemize}

	This is a numbered list.

	\begin{enumerate}
		\item China
		\item Sweden
		\item Canada
	\end{enumerate}

	\subsection{Tables}

	\par This is a simple table.

	\begin{tabular}{ccc}
		\toprule
		Country & GDP & GDP per Capita \\
		\midrule
		USA & 21.43 & 65,298 \\
		China & 14.34 & 10,262 \\
		R.O.Korea & 1.64 & 31,430 \\
		D.P.R.Korea & 0.02 & 1,800 \\
		\bottomrule
	\end{tabular}

	\section{Formula}

	% 短公式
	You need this formula $E=mc^2$

	% 单行公式
	The equation \eqref{Sharon} is a single-line formula:
	\begin{equation}\label{Sharon}
		E=mc^2
	\end{equation}
	This equation \eqref{Acan} is also a single-line formula:
	\begin{equation}\label{Acan}
		\alpha^2+\beta^2 = \gamma^2
	\end{equation}

	% 无编号公式
	This is an index-free formula:
	\[E=mc^2\]
	This is also an index-free formula:
	$$E=mc^2$$

	% 多行公式
	\begin{equation}
		\begin{split}
			\nabla \cdot \mathbf{E} &= \frac{\rho}{\varepsilon_0} \\
    		\nabla \cdot \mathbf{B} &= 0 \\
    		\nabla \times \mathbf{E} &= -\frac{\partial \mathbf{B}}{\partial t} \\
    		\nabla \times \mathbf{B} &= \mu_0\left(\mathbf{J} + \varepsilon_0 \frac{\partial \mathbf{E}}{\partial t}\right)
		\end{split}
	\end{equation}

	% 分类讨论公式
	\begin{equation}
		\begin{cases}
			0&\text{if $x<0$} \\
			x+1&\text{if $0\leq x<1$} \\
			\frac{1}{x^2}&\text{if $x\geq 1$}
		\end{cases}
	\end{equation}

\end{document}